### 2014-08-15 paper/paper.Rmd
adds data-loading scaffolding

@@

>>>>

Luke Fostveldt, Alex Shum, Ian Lyttle, Di Cook

@@

```{r read_me, echo = FALSE}
# Some notes for we authours:
# 
# * If you want to run this code interactively, change your working directory to
# `paper`.
# 
# * If there are packges we are all using, let's load them all once, in the
# load_packages chunk.
# 
# * If there are packages particular to your section, please consider loading
# them there, then detaching at the end of your section.
# 
# * I am being a bit presumptuous by leaving stringr loaded - maybe it makes
# sense to detach it. I'm sure we'll figure out wich way to go with each of our
# loaded packages.
# 
# - IJL
```

```{r load_packages, echo = FALSE, message = FALSE, warning = FALSE}
library(dplyr)
library(stringr)
```

```{r load_data, echo = FALSE, message = FALSE, warning = FALSE}
# This is the scaffolding to import the data
sets <- c("item", "parent", "school", "scoredItem", "student")

# function to build the file names
fn_build <- function(file_name){

  template <- c("2012.rda", "2012dict.rda")

  file_name %>% 
    vapply(str_join, template, template) %>% 
    file.path("..", "data", .)
}

# load the data
sets %>% fn_build %>% lapply(load, .GlobalEnv)

# clean
rm(fn_build, sets)

# function to convert to data-frames
fn_make_df <- function(named_vector){
  data.frame(
    variable = attr(named_vector, "names"),
    description = named_vector,
    row.names = NULL
  )
}

# there's a clever way to do this, but beyond me for naw
dict_item2012 <- fn_make_df(item2012dict) 
dict_parent2012 <- fn_make_df(parent2012dict) 
dict_school2012 <- fn_make_df(school2012dict) 
dict_scoredItem2012 <- fn_make_df(scoredItem2012dict) 
dict_student2012 <- fn_make_df(student2012dict)

# clean
rm(fn_make_df)
#rm(item2012dict, parent2012dict, school2012dict, scoredItem2012dict, student2012dict)
```
